Verifying Demonstrations

### 2020-07-03 paper/intro.tex
Emphasizes that we don't achieve _full_ TF

Our last contribution is another version of the protocol, one which uses 
bit-by-bit transmissions as traditionally done with \ac{DB} protocols.
We achieve all properties except \ac{DBTF} resistance.
We see this contribution as merely for the sake of completion, as the previous 
contributions are slightly more efficient.

>>>>

Our last contribution is another version of the protocol, one which uses 
bit-by-bit transmissions as traditionally done with \ac{DB} protocols.
We achieve all properties except (full) \ac{DBTF} resistance.
We see this contribution as merely for the sake of completion, as the previous 
contributions are more efficient.
